\begin{center}

\textbf{Curriculum Vitae}

Dr. Andrew P. White

Department of Physics, University of Texas at Arlington, Box 19059, Arlington, TX 76019

E-mail:awhite@uta.edu

Phone: (817) 272-2812 (office), (817) 272-2266 (Physics department)

FAX: (817) 272-3637

\end{center}


\subsection{EDUCATION AND TRAINING}
\begin{itemize}
\item{
\textbf{Ph.D. in Experimental High Energy Physics, Westfield College, University of London (1969-1972) }
}

\item{
\textbf{B.Sc (Honours) Physics, University of  Southampton, U.K., (1965-1969) }
}
\end{itemize}
\subsection{RESEARCH AND PROFESSIONAL EXPERIENCE}
\begin{itemize}
\item{
\textbf{Professor of Physics,  University of Texas at Arlington (1991-present)}
}

\item{
\textbf{Research Scientist, High Energy Physics Group, University of Florida (1985-1991) } 
}

\item{
\textbf{Staff Physicist, High Energy Physics Group, Imperial College, University of London (1973-1985) 
(this included a period of work based at SLAC 1974-1976) }
} 

\item{
\textbf{Research Associate, HEP, Westfield College, University of London (1972-1973) } 
}

\item {
\textbf{Research Assistant, HEP, Westfield College, University of London (1969-1972) } 
}
\end{itemize}

\subsection[PUBLICATIONS:]{\color{black} PUBLICATIONS:}
\begin{enumerate}

\item{{{ATLAS }}Collaboration, ``Observation of a new particle in the search for the Standard Model Higgs boson 
with the ATLAS detector at the LHC '', Phys. Lett. B 716 (2012) 1-29.}

\item{{{ATLAS and CMS}}Collaborations,``Search for invisible decays of a Higgs boson using vector-boson fusion 
in $pp$ collisions at $\sqrt{s}=8$ TeV with the ATLAS detector''JHEP01 (2016) 172.}

\item{{{ATLAS and CMS}}Collaborations, ``Search for Invisible Decays of the Higgs boson at the LHC'',
A. White on behalf of the ATLAS and CMS Collaborations, Proceedings of LHCP 2015 Conference, St. Petersburg, Russia, August 2015}

\item{{\color{black}} {International Linear Collider, Technical Design Report, Volume 4, Detectors; 
http://www.linearcollider.org/ILC/Publications/Technical-Design-Report} }}

\item{``Experimental tests of particle flow calorimetry'', Felix Sefkow, Andy White, et al, Rev. Mod. Phys. 88, 015003 (2016)}

\item{''Development of a Gas Electron Multiplier-based Digital Hadron Calorimeter'', A White et al 2012 J. Phys.: 
Conf. Ser. 404 01203}

\end{enumerate}


\subsection[SYNERGISTIC ACTIVITIES]{\textcolor{black}{SYNERGISTIC ACTIVITIES}}

\begin{enumerate}

\item {
\textbf{\textcolor{black}{D0 Intercryostat Detector:}}\textcolor{black}{: Invented the Intercryostat Detector for D0 used to 
correct the energies of particle/jets due to substantial losses in dead material. }}

\item {
\textbf{\textcolor{black}{GEM-based Digital Hadron Calorimetry:}}\textcolor{black}{: Invented and developed the concept of Gas Electron Multiplier
based digital calorimetry for high resolution jet energy measurements at colliders} }

\item {
\textbf{\textcolor{black}{SiD Spokesperson:}}\textcolor{black}{: Spokesperson for the SiD Detector Concept for the International 
Linear Collider; leading and guiding all aspects of the concept towards its realization}}

\item {
\textbf{\textcolor{black}{CALICE Collaboration:}}\textcolor{black}{: North American Representative for the CALICE Collaboration
developing all aspects of calorimetry for future linear colliders}.}

\item {
\textbf{\textcolor{black}{CERN RD51 Collaboration:}}\textcolor{black}{ Deputy Chair and Member of the Management Board for RD51
 - Micro-pattern Gas Detector Collaboration.}}
 
\end{enumerate}

\subsection[COLLABORATORS AND CO{}-EDITORS]{{\textcolor{black}{COLLABORATORS AND
CO-EDITOR}}\textcolor{black}{S}}
\begin{itemize}
\item {
\textbf{\textcolor{black}{ATLAS Experiment: }}\textcolor{black}{Ketevi Assamagan – BNL, Joey Huston (MSU), Bill Quayle - U.Wits, 
Young Kee Kim - U.Chicago, Tae Hong - U.Pittsburgh, Elliot Lipeles - U. Penn., Alexander Madsen - DESY }}

\item {
\textbf{\textcolor{black}{SiD Detector Concept: }}\textcolor{black}{M.Breidenbach, J.Jaros, T. Barklow – SLAC, M.Demarteau - ANL, 
H.Weerts – ANL, J. Brau - U.Oregon, J.Strube - PNNL, M.Stanitzki (DESY)}}

\item {
\textbf{\textcolor{black}{CALICE Collaboration: }}\textcolor{black}{F.Sefkow - DESY, J.Repond - ANL, K.Kawagoe - Kyushu U.}}

\item {
\textbf{\textcolor{black}{RD51 Collaboration: }}\textcolor{black}{M. Hohlman - FIT}}
\end{itemize}

\subsection[GRADUATE AND POSTDOCTORAL ADVISORS AND ADVISEES]{\color{black} GRADUATE AND POSTDOCTORAL ADVISORS AND
ADVISEES}

\begin{enumerate}
\item \textbf{\textcolor{black}{Mark }}\textbf{\textcolor{black}{Sosebee}}\textcolor{black}{, Ph.D.,
}\textit{\textcolor{black}{University of Texas at Arlington,}}

\item \textbf{\textcolor{black}{Richard Bonde}}\textcolor{black}{, Ph.D., }\textit{\textcolor{black}{University of
Texas at Arlington}}\textcolor{black}{, }\textbf{\textcolor{black}{2015}}

\item \textbf{\textcolor{black}{Carlos Medina}}\textcolor{black}{, M.S., }\textit{\textcolor{black}{Colorado School of 
Mines,}}\textbf{\textcolor{black}{ 2010}}

\item \textbf{\textcolor{black}{Fajer Jafaari}}\textcolor{black}{, M.S., }\textit{\textcolor{black}{University of Texas 
at Arlington and Tarrant County College,}}\textbf{\textcolor{black}{ 2010}}

\end{enumerate}

\begin{enumerate}

\item {
\textbf{Dr. Seongtae Park}, Postdoctoral Fellow\newline
\textit{University of Texas at Arlington, }\textbf{2010-2014.}}

\item {
\textbf{Dr. Mark Sosebee}, Postdoctoral Fellow\newline
\textit{University of Texas at Arlington, }\textbf{1996-present.}}

\end{enumerate}

