\documentclass[10pt]{article}
\usepackage[letterpaper,top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{bbding}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace} 
\usepackage{rotating}
\usepackage{multirow}
\usepackage[compact]{titlesec}

%\pagenumbering{arabic}
%%\usepackage{atlasphysics}
%\date{}
\newcommand{\tanb}{$\tan \beta$}
\newcommand{\too}{$\rightarrow$}
%\newcommand{\invfb}{$fb^{-1}$}
\newcommand{\Hp}{$H^{+}$}
\newcommand{\ttbar}{$t\overline{t}$}
\newcommand{\Bz}{$B^0$}
\newcommand{\Bu}{$B^+$}
\newcommand{\KS}{$K^0_{S}$}
\newcommand{\FourS}{$\Upsilon(4S)$}
\newcommand{\jpsi}{$J\mskip -3mu/\mskip -2mu\psi\mskip 2mu$}
%\title{Multiple Beyond Standard Model Search on the ATLAS Experiment at the Large Hadron Collider}
%\title{Search for Beyond Standard Model Phenomena using the Higgs} 

\author{Haleh Hadavand}

%\pagestyle{plain}                     

%\textfloatsep  0in

%\belowcaptionskip 0in
%\abovecaptionskip 0in
\begin{document}
\def\@tablebox#1{\begin{tabular}[t]{@{}l@{}}#1\end{tabular}}

\newenvironment{llist}{\begin{list}{}{\setlength
 \labelwidth{1in}\setlength\leftmargin{\labelwidth}\addtolength
 \leftmargin{\labelsep}\itemsep 5pt plus 2pt minus 2pt
 \parsep 10pt plus 2pt minus 2pt
 %% Set the depth of the title to 0 in case more than one line.
 %% If the title takes more lines than the body, you lose.
 \def\sectiontitle##1{\setbox\@title=\hbox{{\it\@tablebox{##1}}}\dp\@title=0pt
   \item[\copy\@title]\ifdim\wd\@title>\labelwidth
   \leavevmode \\* \else \fi}
 \def\makelabel##1{##1\hfill}}}{\end{list}}

\def\employer{\@ifstar{\@semployer}{\@employer}}
\def\@employer#1{\par{\sc #1}}
\def\@semployer#1{{\sc #1}\\}

% The location is always flush right.  It is moved to the next
% line if there is not room left on this one.··
% See the TeXbook Chapter 14.
\def\location#1{{\bf{}\unskip\nobreak\hfill\penalty50\hskip2em
  \hbox{}\nobreak\hfill \hbox{#1}\finalhyphendemerits=0 \\}}
\def\dates#1{{\em #1}\\[2pt]}

\begin{center} {\bf\Large Haleh Hadavand }\end{center}
%{\begin{tabular}[t] {@{}l @{\hspace{3cm}}l} 

%University of Texas Arlington \\
%Department of Physics\\
%P.O. Box 19059\\
%Arlington, TX, 76019  &{\bf e-mail: hadavand@uta.edu} \\
%\end{tabular}}

\subsection*{Education and Training}

\par{\sc {\bf Undergraduate: University of Maryland College Park}}
\location{ College Park, MD}
\dates{Sep 1995 - Jun 1999}
Degree: BS in Physics, June 1999.\\ 
\par{\sc {\bf Graduate:  University of California San Diego}}
\location{ La Jolla, CA}
\dates{Aug 1999 - Sept 2005}
Degree: Ph.D. in High Energy Physics
Dissertation: ``The Measurement of CP Asymmetries in the Three-body Charmless $B_d$ Meson Decay to $K^0_S K^0_S K^0_S$ at BABAR ''\\
Thesis adviser: David MacFarlane. \\

\subsection*{Research and Professional Experience} 
\par{\sc \bf{Assistant Professor}}
\location{ University of Texas Arlington} 
\dates{Nov 2014 - Present}
\par{\sc \bf{Research Faculty}}
\location{ University of Texas Arlington} 
\dates{July 2012 - Oct 2014}
\par{\sc \bf{Postdoctoral Fellow}}
\location{ Southern Methodist University} 
\dates{Sept 2005-July 2012}
\par{\sc \bf{Graduate Research Assistant}}
\location{ UCSD on BABAR experiment} 
\dates{Jun 1999 - Sept 2005}
\subsection*{Relevant Publications}
\renewcommand\refname{\vskip -1.5cm}
\begin{thebibliography}{99}

%\bibitem{atl2014} {} The ATLAS Collaboration, "Search for charged Higgs bosons decaying via $H^{\pm} \rightarrow \tau^{\pm}\nu$ in fully hadronic final states using pp collision data at $\sqrt{s}$ = 8 TeV with the ATLAS detector'', ATL-COM-PHYS-2014-372 (2014).
\bibitem{atl2014} {} The ATLAS Collaboration, "Search for charged Higgs bosons decaying via $H^{\pm} \rightarrow \tau^{\pm}\nu$ in fully hadronic final states using pp collision data at $\sqrt{s}$ = 8 TeV with the ATLAS detector'', JHEP03 (2015) 088.
\bibitem{atl2013} {} The ATLAS Collaboration, "A Search for Charged Higgs Bosons in the $\tau$ +jets Final State with pp Collision Data Recorded at $\sqrt  s = 8$ TeV with the ATLAS Experiment'', ATLAS-CONF-2013-090 (2013).
\bibitem{atl1} {} The ATLAS Collaboration, ``Search for extra dimensions using diphoton events in 7 TeV proton-proton collisions with the ATLAS detector", Phys.\ Lett.\ B {\bf 710}, 538-556 (2012).
\bibitem{atl1-conf} {} The ATLAS Collaboration, ``A Search for High Mass Diphoton Resonances in the Context of the Randall-Sundrum Model in $\sqrt s=7$ TeV pp Collisions", ATLAS-CONF-2011-044 (2011).

\bibitem{atl2} {} The ATLAS Collaboration, ``Search for Diphoton Events with Large Missing Transverse Energy in 7 TeV Proton-Proton Collisions with the ATLAS Detector'', Phys.\ Rev.\ Lett.\  {\bf 106}, 121803 (2011).

%\bibitem{atl6}  {}Peter Renkel, Haleh Hadavand, Robert Kehoe, ``The Gatherer - a mechanism for integration of monitoring data in ATLAS'', {}, J.\ Phys.\ Conf.\ Ser.\  {\bf 219}, 022043 (2010).

\bibitem{atl5a} {} Ilchenko, Y., Cuenca-Almenar, C. , Corso-Radu, A., Hadavand, H.  Kolos, S,  Slagle, K.,  Taffard, A.,``Data Quality Monitoring Display for ATLAS experiment'', J.\ Phys.\ Conf.\ Ser.\  {\bf 219}, 022035 (2010).

\bibitem{atl5}
  H.~Hadavand [ ATLAS Collaboration ],
  ``Commissioning of the ATLAS offline software with cosmic rays'',
  J.\ Phys.\ Conf.\ Ser.\  {\bf 119}, 032021 (2008).

\bibitem{atl5b}
  S.~Kolos, A.~Corso-Radu, H.~Hadavand, M.~Hauschild, R.~Kehoe,
  ``A software framework for Data Quality Monitoring in ATLAS'',
  J.\ Phys.\ Conf.\ Ser.\  {\bf 119}, 022033 (2008).

%\bibitem{atl7}  {}Alina Corso-Radu, Haleh Hadavand, Michael Hauschild, Bob Kehoe, Serguei Kolos, ``Data Quality Monitoring Framework for the ATLAS Experiment at the LHC'', IEEE Trans.\ Nucl. Sci.\ {\bf 55}, 1 (2008).

\bibitem{bab1} {}B.~Aubert {\it et al.}  [BABAR Collaboration],
``Branching Fraction and CP Asymmetries in \Bz \too \KS \KS \KS'',
  Phys.\ Rev.\ Lett.\  {\bf 95}, 011801 (2005).

\bibitem{bab0} {}B.~Aubert {\it et al.}  [BABAR Collaboration], ``Measurement of the \Bu/\Bz production ratio from the \FourS meson using \Bu $\rightarrow$ \jpsi K$^+$ and \Bz $\to$ \jpsi \KS decays'', {}Phys.\ Rev.\ D {\bf 69}, 071101 (2004).
``New Physics results from the BABAR Collaboration'', July 2005.
\section*{Synergistic Activities}
\renewcommand\refname{\vskip -1.5cm}

\subsection*{Invited Talks}
\bibitem{t11}  Lake Louise Winter Institute, Lake Louise, Alberta, Canada, ``Beyond-the-Standard Model Higgs and Invisible Higgs Decays Using the ATLAS Experiment'', February 2014.

\bibitem{t10}  Photon 2011 Conference at Spa, Belgium, ``New Physics Searches with Photons at the ATLAS and CMS Experiments'', May 2011.

%\bibitem{t9}  Seminar at Southern Methodist University, Dallas, ``New Physics Results with Diphotons at the ATLAS Experiment'', April 2011.

%\bibitem{t8} Talk at Southwest US ATLAS Physics Jamboree, ``Search for Graviton and other Exotic Particles'', April 2011.

\bibitem{t7}  Beyond Standard Model Physics Conference,  Boston, MA., ``Beyond the Standard Model Photon Physics at the ATLAS and CMS Experiments at the Large Hadron Collider'', June 2009.

%\bibitem{t6}  Computing in High Energy and Nuclear Physics (CHEP) Victoria, British Columbia, Canada, ``Commissioning of the ATLAS Offline Software with Cosmic Rays'', September 2007.

%\bibitem{t5}  The 13th International Conference on Supersymmetry and Unification of Fundamental Interactions, SUSY 2005, Durham, United Kingdom, 
\end{thebibliography}
\subsection*{Leadership Experience}
\begin{itemize}
%\item 35 Ton Monitoring Developer and Contact on Long Baseline Neutrino Facility at Fermilab.
\item Charged Higgs convenor on the ATLAS experiment.
\item Co-editor of paper and conference note on extra dimension diphotons resonances ~\cite{atl1,atl1-conf}.

%\item Interim co-editor and analysis contact for paper {\it Search for Diphoton Events with Large Missing Transverse Energy in 7 TeV Proton-Proton Collisions with the ATLAS Detector}~\cite{atl2}.
%\item Jet/$\mathbf{E_T^{miss}}$ and Calorimeter Monitoring Contact Person on the ATLAS experiment.
%\item Data Quality Acquisitions Manager on the \BABAR\ experiment.
\end{itemize}
%\subsection*{Honors/Awards}
%University of San Diego Fellowship For Graduate Studies, Phi Beta Kappa National Honor Society, University of Maryland Honors Program.

\section*{Collaborators and Co-editors}
Maria Pilar Casado, Universitat Autònoma de Barcelona, Arnaud Ferrari, Uppsala University, Thomas Junk, Fermilab, Anna Kopf, Freiburg University, Allison McCarn, Univerisity of Michigan, Henrik Ohman, Uppsala University,
Michael Pitt, Weizmann Institute of Science, John Parsons, Columbia University, Nikolaos Rompotis, University of Wisconsin, Jana Schaarschmidt, Weizmann Institute of Science, Stephen Sekula, Southern Methodist University,
Camila Rangel Smith, Uppsala University, Michelle Stancari, Fermilab.

\section*{Graduate and Postdoctoral Advisors and Advisees}
Rozmin Daya-Ishmukhametova, University of Massachusetts - Amherst, Yuriy Ilchenko, UT Austin, Renat Ishmukhametov, Ohio State University,Bob Kehoe, 
Southern Methodist University, Ryszard Stroynowski, Southern Methodist University.

\end{document}
