\begin{center}

{\bf Jaehoon Yu}

Department of Physics, University of Texas at Arlington, Box 19059, Arlington, TX 76019

E-mail:jaehoonyu@uta.edu, URL:http://www-hep.uta.edu/$\sim$yu/

Phone: (817) 272-2814 (office), -2266 (physics dept.), (817)808-9605 (cell)

FAX: (817) 272-3637 (dept)

\end{center}
%
{\underline{\underline{{\bf EDUCATION AND TRAINING}}}}
\begin{itemize}[noitemsep]
\item {\bf Research Associate}{, Fermi National Accelerator Laboratory,} {\bf 1996-1998}
\item {\bf Research Fellow}{, University of Rochester,} {\bf 1993-1996}
\item {\bf Ph.D.}{, Physics, State University of New York, Stony Brook, } {\bf 1993}
\item {\bf M.S.}{, Physics,State University of New York, Stony Brook, } {\bf 1992}
\item {\bf M.A.}{, Physics, Korea University, Seoul, South Korea,} {\bf 1985}
\item {\bf D.S.}{, Physics, Korea University, Seoul, South Korea,} {\bf 1983}
\end{itemize}
%
{\underline{\underline{{\bf RESEARCH AND PROFESSIONAL EXPERIENCE}}}}
\begin{itemize}[noitemsep]
\item {\bf Professor}{, University of Texas at Arlington, } {\bf 2012--present}
\item {\bf Associate Professor}{, University of Texas at Arlington, } {\bf 2006--2012}
\item {\bf Assistant Professor}{, University of Texas at Arlington, } {\bf 2001--2006}
\item {\bf Associate Scientist}{, Fermi National Accelerator Laboratory, }{\bf 1998-2001}
\end{itemize}
%
{\underline{\underline{{\bf SELECTED PUBLICATIONS}}}}
\begin{enumerate}[noitemsep]
\item ATLAS Collaboration, “Measurement of exclusive $\gamma\gamma\rightarrow W^{+}W^{-}$ Production and search for exclusive Higgs boson production in pp collisions at $\sqrt{s}=8$~TeV using the ATLAS detector”, Phys. Rev. {\bf D 94}, 032011 (2016)
\item ATLAS Collaboration, “Measurements of the Higgs boson production and decay rates and coupling strengths using pp collision data at √s=7 and 8 TeV in the ATLAS experiment,” arXiv:1507.04548 [hep-ex]
\item Georges Aad et al., ATLAS Collaboration, “Study of (W/Z)H production and Higgs boson couplings using HWW decays with the ATLAS detector,” JHEP 1508 (2015) 137.
\item Keisuke Fujii et al., Linear Collider Physics Panel, “Physics Case for the International Linear Collider,” arXiv:1506.05992 [hep-ex].
\item CMS and ATLAS Collaborations, “Combined Measurement of the Higgs Boson Mass in pp Collisions at √s=7 and 8 TeV with the ATLAS and CMS Experiments,” Phys.Rev.Lett. 114 (2015) 191803.
\item Georges Aad et al., ATLAS Collaboration, “Search for a Charged Higgs Boson Produced in the Vector-Boson Fusion Mode with Decay H±W±Z using pp Collisions at √s=8  TeV with the ATLAS Experiment,” Phys.Rev.Lett. 114 (2015) 23, 231801.
\item C. Adams et al., LBNE Collaboration, “The Long-Baseline Neutrino Experiment: Exploring Fundamental Symmetries of the Universe,” arXiv:1307.7335 (2014)
\item H. Frisch, C. Hast, E. Ramberg, M. Artuso, A. Seiden, M. Wetstein, M.C. Sanchez \& J. Fast, et al, “Compendium of Instrumentation Frontier Whitepapers on Technologies for Snowmass 2013” 
\item Georges Aad et al., ATLAS Collaboration, “Search for dark matter in events with heavy quarks and missing transberse momentum in pp collisions at √s =7 TeV with the ATLAS detector” arXiv:1410.4031 (2014)
\item Georges Aad et al., ATLAS Collaboration, “Search for neutral Higgs boson of the minimal supersymmetric standard model in pp collisions at √s =8 TeV with the ATLAS detector” JHEP 1411 (2014) 056
\end{enumerate}
%
{\underline{\underline{{\bf SYNERGISTIC ACTIVITIES}}}}
\begin{enumerate}[noitemsep]
\item {\bf Aug. 2016 – present:} Executive Board member, WA105 experiment at CERN
\item {\bf Nov. 2015 – present:} Institutional Board member, ICARUS experiment at CERN/Fermilab
\item {\bf Sept. 2015 – present:} DUNE Beyond the Standard Model physics group co-convener
\item {\bf Mar. 2015 – present:} Institutional Board representative, Deep Underground Neutrino Experiment at Fermilab
\item {\bf Aug. 2013 – Jan. 2015:} LBNE R\&D Coordinating committee co-convener
\end{enumerate}
%
{\underline{\underline{{\bf COLLABORATORS}}}}{:ATLAS, CALICE, SiD, LBNE, LArIAT and ORKA Collaborations}\\
%
{\underline{\underline{{\bf GRADUATE AND POSTDOCTORAL ADVISORS}}}}
\begin{itemize}[noitemsep]
\item {\bf Dr. Robert Bernstein}, Fermilab, PostDoctoral Advisor:{\bf 1996--1998}
\item {\bf Prof. Frederick Lobkowitz (deceased)}, Univ. of Rochester, PostDoctoral Advisor:{\bf 1993--1996}
\item {\bf Prof. Robert L. McCarthy}, SUNY Stony Brook, Thesis Advisor:{\bf 1988--1993}
\end{itemize}
%
{\underline{\underline{{\bf POSTDOCTORAL ADVISEES}}}}
\begin{enumerate}[noitemsep]
\item {\bf Dr. Animesh Chatterjee}, Postdoctoral Fellow, University of Texas at Arlington, {\bf 2014-present.}
\item {\bf Dr. Justin Griffiths}, Postdoctoral Fellow, University of Texas at Arlington, {\bf 2012-present.}
\item {\bf Dr. Seongtae Park}, Senior Postdoctoral Fellow, University of Texas at Arlington, 
{\bf 2010-2014}
\item {\bf Dr. Hyunwoo Kim}, Postdoctoral Fellow, University of Texas at Arlington, {\bf 2004-2007, 
currently an associate scientist at Fermilab}
\item {\bf Mr. Sudhamshi Reddy}, Software Engineer, University of Texas at Arlington, 
{\bf 2007-2009, currently on UTA Computer Science and Engineering Ph.D. candidate}
\end{enumerate}
%
{\underline{\underline{{\bf GRADUATE STUDENT ADVISEES}}}}
\begin{enumerate}[noitemsep]
\item {\bf Garrett Brown}, Ph.D., Univ. of Texas at Arlington, {\bf 2016 —- present}
\item {\bf Last Feremenga}, Ph.D., Univ. of Texas at Arlington, {\bf expected to graduate in 2016}
\item {\bf Heeyeun Kim}, Ph.D., Univ. of Texas at Arlington, {\bf 2015 —- Researcher at Harvard Medical School}
\item {\bf Dr. Jacob Smith}, Ph.D., Univ. of Texas at Arlington, {\bf 2013--PostDoc at U. of Maryland}
\item {\bf Dr. Hyeonjin Kim}, Ph.D., Univ. of Texas at Arlington, {\bf 2010--PostDoc at U. of 
Stockholm, Sweden}
\item {\bf Dr. Venkatesh Kaushik}, Ph.D., Univ. of Texas at Arlington, {\bf 2007-- ${\rm EMC^{2}}$}
\item {\bf Jacob Smith}, M.S., Univ. of Texas at Arlington, {\bf 2010--Continued into 
the Ph.D. program at UTA}
%\item {\bf Venkatesh Kaushik}, M.S., Univ. of Texas at Arlington, {\bf 2004--Continued 
%into the Ph.D. program at UTA}
%\item {\bf Shahnoor Habib}, M.S., Univ. of Texas at Arlington, {\bf 2003--Continued into 
%the Ph.D. program in Canada}
\end{enumerate}
