\section {Current and Pending Support}\subsection{\bf {PI: Jaehoon Yu}}\subsubsection {Current}\begin{enumerate}\item {Funding Sponsor: Department of Energy}\begin{itemize}\item {Proposal ID: 0000209151 }\item{Title: Research on Elementary Particle Physics}\item {Total cost: \$2,520,000}\item{Award Period: 5/1/2014 Ð 3/31/2017}\item{ Time commitment: 2.0 months per year}\item{ Project Abstract: The major goals of this project are to carry out various research tropics in understand the fundamental constituents of matter and the forces between them.  We focus on ATLAS experiment and the preparation of the International Linear Collider as well as understanding neutrino oscillation behaviors through contribution to the intensity frontier experiments, LArIAT, MiniBooNE and DUNE.}\end{itemize}\item {Funding Sponsor: National Cancer Institute, National Health Institute}\begin{itemize}\item {Award Number: 1R15CA199020-01A1}\item{Title: Boosting photo-induced cancer therapies through real-time image guidance}\item {Total cost: \$  415,336}\item{Award Period: 4/1/2016 Ð 3/31/2019}\item{ Time commitment: 0.2 months per year}\item{ Project Abstract: we propose to use the position-sensitive gas electron multiplier (GEM) detector and advanced spatiotemporal image processing to enable real-time image guided PITs. The GEM technology is a recent advance of the revolutionary digital imaging of gas detectors using multiwire proportional chambers (MWPC), which won Georges Charpak a Nobel Prize for Physics in 1992. The advantages of GEM-based devices include: intrinsic spatial resolution of 50 {$\mu m$} or better; rate capability lager than 1MHz/mm^{2}; easy achievable gains above 10^{5}; allowing detection of single electrons; efficiency for minimum ionizing particles close to 100\%. In additional to its excellent detection performance, the flexibility of GEM can be used for a miniature device with the easy integration of an NIR fiber for therapeutic purpose. In this project, for the first time, we propose to develop a multifunctional device using GEM technology for PITs, called Ò{\bf Beta Image Guided Light-Induced Therapeutic devicE (BIGLITE)}Ó, which can achieve {\bf simultaneous imaging and photo-induced therapy}.}\end{itemize}\item {Funding Sponsor: National Science Foundation}\begin{itemize}\item {Award Number: 1639157}\item{Title: Support for Biennial African School of Fundamental Physics 2016}\item {Total cost: \$ 28,215}\item{Award Period: 7/1/2016 Ð 6/30/2017}\item{ Time commitment: 0.01 months per year}\item{ Project Abstract: This proposal is in support of the forth school in the biennial series. The aim of the school is to build the capacity to harvest, interpret, and exploit the results of current and future physics experiments with particle accelerators, and to increase proficiency in related applications such as medicine, and technologies, such as grid computing. The schools are based on a close interplay between theoretical, experimental and applied physics.  The organizing committee consists of a number of people key in the above areas, from both inside and outside Africa. Sub-Saharan Africa is under-represented in sub-atomic physics and this school will serve to provide more opportunities for students to become aware of and to participate in this field. }\end{itemize}\item {Funding Sponsor: CNRS, France}\begin{itemize}\item {Award Account Number: 1263101510}\item{Title: MOU for Research on WA105 Dual Phase Detector and DUNE}\item {Total cost: \$36,728}\item{Award Period: 10/1/2015 Ð 12/31/2017}\item{ Time commitment: 1.0 months per year}\item{ Project Abstract: The major goal of this project is to contribute to the setup of WA105 and understanding DUNE cryostats.}\end{itemize}   \item {Funding Sponsor: ETH, Switzerland}\begin{itemize}\item {Award Account Number: 1263101510}\item{Title: MOU for Research on WA105 Dual Phase Detector and DUNE}\item {Total cost: \$36,728}\item{Award Period: 10/1/2015 Ð 12/31/2017}\item{ Time commitment: 1.0 months per year}\item{ Project Abstract: The major goal of this project is to contribute to the setup of WA105 and understanding DUNE cryostats. These funds enable the PI to cover the cost for a local stay during an extended stay at CERN.}\end{itemize}\item {Funding Sponsor: ETH, Switzerland}\begin{itemize}\item {Award Account Number: NA}\item{Title: MOU on Research on WA105 dual phase Prototype LAr Detector}\item {Total cost: \$10,000}\item{Award Period: 1/1/2016 Ð 12/31/2017}\item{ Time commitment: 0.5 months per year}\item{ Project Abstract: The major goal of this project is to contribute to the setup of WA105 and understanding DUNE cryostats.  These funds enable the PI to buy out teaching for two semesters for an extended stay at CERN.}\end{itemize}\item {Funding Sponsor: Fermi National Accelerator Laboratory}\begin{itemize}\item {Award Account Number: NA}\item{Title: Application for Neutrino Physics Center Fellowship}\item {Total cost: \$10,000}\item{Award Period: 7/1/2016 Ð 6/30/2017}\item{ Time commitment: 1.5 months per year}\item{ Project Abstract: The major goals of this project are to understand the behavior of the membrane cryostat, develop and design the beam hadron monitor and optimize the beam line components for DUNE experiment. These funds enable the PI to contribute directly to DUNE experiment through an extended stay at FNAL.}\end{itemize}

\item {Funding Sponsor: Brookhaven National Laboratory, Department of Energy}\begin{itemize}\item {Award Number:}\item{Title: Development of SiPM Coupling with Scintillation Counters for Range Stack Detector }\item {Total cost: \$46,000}\item{Award Period: 10/1/2013 Ð 9/30/2016}\item{ Time commitment: 0.1 months per year}\item{ Project Abstract: The Range Stack (RS) in ORKA detector plays an essential role in particle identification, especially the pions from Kaon decays from muons.  It must be able to measure the energy, range and decay sequence of charged particles emerging from the target with a good position resolution.  In addition, it must able to assist photon veto (PV) detector by identifying them with good efficiency for the photons converting before getting into the PV system.}\end{itemize}\end{enumerate}                                   