\begin{center}
\textbf{Dr. Andrew P. White}
\end{center}

1) I am the Lead PI on the current DoE proposal (pending), "Research in Elementary
Particle Physics". My requested support for 4/1/2017 through 3/31/2020 is \$XXXXXXX.
2.0 months Summer salary each year.  \\

Project Abstract: \\
*** abstract for the new proposal goes here ***\\

2) I am the PI on current DoE HEP grant DESC0011686 for \$890,000 for the period 4/1/2016 through 3/31/2017.
This grant supports the activities of the UTA HEP group for : summer salaries for two months for four
faculty (White, De, Brandt, Yu), one postdoc, four graduate students, foreign travel and 
COLA, and M\&S. Activities include Higgs and supersymmetry analyses for ATLAS, ATLAS
Tile Calorimeter calibration, radiation damage studies, and electronics upgrades, 
ATLAS distributed computing and Tier-2, SiD Consortium leadership and hadron calorimeter
development. This grant also supports work on DUNE/LBNE, LArIAT. \
2.0 months Summer salary.\\

Project Abstract: \
This project supports the work of the UTA HEP group for the Energy and Intensity Frontiers.
For the Energy Frontier, activities for the ATLAS experiment include leadership in computing and software,
support for the operation and calibration of the Tile Calorimeter, physics studies in the SUSY and Higgs sectors,
and upgrade work on TDAQi and low voltage power supplies. Also for the Energy Frontier, we have a Spokesperson
role in the SiD Consortium for the International Linear Collider. Activities for SiD include 
the development of the design of the SiD Detector, establishing the SiD Consortium as a precursor to a full detector collaboration,
promotion and coordination all aspects of detector R\&D and physics and performance studies, and 
representation of SiD within the HEP community nationally and internationally.
For the Intensity Frontier efforts include optimization of LBNF beam line for DUNE,
Design and construction of proton beam alignment monitor (PBAM) for DUNE, aka hadron monitor,
optimization of Optical Coupling for DUNE photo detectors, DUNE 35t Data Analysis and Operations,
studies for subGeV Dark Matter, Phase I LArIAT experiment data analyses, MiniBooNE beam dump data analysis,
and contributions to Fermilab onsite long baseline experiments.
 \\




