\textbf{Energy Frontier - International Linear Collider}

\item{\bf Cumulative - 3 years}

\begin{itemize}

\item{{\bf Senior Personnel}: One month summer salary for each year for White is requested at the current rate of \$127,386 per 9 month academic year, 
equivalent to \$14,154 per month.  The total request for this item is 3 summer months at \$42,462. The fringe benefit rate is 30\% of the request.  
The indirect rate for this item is the agreed on-campus rate of 51.5\%.}

\item {{\bf Undergraduate Students}: Undergraduate students Andrew Myers and Ross McCoy (in Year 1, and other students in Years 2 and 3) 
will continue their present work on the SiD simulation and physics studies.
Support for two undergraduates is requested at the base rate \$5,000, equivalent to \$12.5 per hour, 10 hours a week for 40 weeks per year.  
The total cost for this request for 3 years is \$30,000.  The fringe benefit rate for an undergraduate student is 8.5\%.

\item{{\bf Travel}: A total of \$42,000 for 3 years is requested to support White's travel as SiD Spokesperson - 3 trips to Japan at \$3,000, 3 trips to
Europe at \$3,000, both of these for regional LC meetings and SiD recruiting; 3 international conferences at \$3,000, 3 domestic conferences 
at \$2,500, and 3 domestic SiD Workshops at \$2,500.

\item {{\bf M\&O}: A limited amount for maintenance and operation cost of \$2,500 per annum is requested to support various costs.   Total cost \$7,500.
This request is subject to on-campus indirect rate of 51.5\%.}

\item {{\bf Total Fringe Benefit}: The total 3 year cost for the fringe benefits is \$15,675.}

\item {{\bf Total Indirect}: The total indirect cost computed using the on-campus (51.5\%) and off-campus (26\%) rates is \$56,973}

\item {{\bf Total for Year 1}: The total request for Years 1,2, and 3 ILC for White is \$188,396.}

\end{itemize}
