\subsection{Budget Justification for the ATLAS Program}
{\bf Preamble:} This section provides the budget justifications for the ATLAS experiment and includes the PIs White, De, Brandt, Farbin, and Hadavand.  A canonical cost of living adjustment rate of 3\% is applied to all salaries in years two and three. 
The total budget for ATLAS for the three years is \$2,656,887.

The tasks carried out on-campus versus off-campus incur substantially different indirect rates – 51.5\% on-campus versus 26\% off-campus. 

% ATLAS- Year 1 justification 
\begin{enumerate}
\item{Year 1}
\begin{itemize}
\item{{\bf Senior Personnel}: Summer salary for PIs requested is \$97,222.   The fringe benefit rate is 30\% of the request.  The indirect rate for this item is the agreed on-campus rate of 51.5\%.}

\item {{\bf Postdoctoral Researcher}: A request for 3.1 postdoctoral fellows is made using the base salary of \$54,000 per annum for a total of \$167,400.  The fringe benefit rate is 30\% of the request.  Since it is anticipated to have 1 postdoctoral fellow on-campus and 2.1 off campus at CERN, the indirect rates for this cost are 51.5\%  and 26\% respectively for the relevant portion of the cost.} 

\item{{\bf Graduate Students}: A request for 4 graduate students support is made at the base rate of \$24,000 per annum for a total of \$96,000.   The fringe benefit rate is 10\% of the request.  Since it is anticipated to have 2 graduate students on-campus and 2 off-campus at CERN, indirect rate for this cost 51.5\% and 26\% respectively.}

\item {{\bf Undergraduate Students}: A request of 3 undergraduate students support is made at the base rate of \$5,000 per annum for a total of \$15,000. They will be located on-campus therefore an indirect rate of 51.5\% is applied to this rate. }

\item{{\bf Travel and Cost of Living Adjustment}: A total request of \$110,700 for travel and COLA support for postdoctoral fellow and graduate student is made. Of this amount, the travel support is \$49,500.  An indirect rate for this cost of 26\% off-campus is applied. }

\item {{\bf STEM Tuition}: Graduate student tuition support for one student is requested at the rate of \$9,140 per annum for a total of \$36,560.  This cost does not incur indirect cost.}

\item {{\bf M\&O}: A modest request for maintenance and operation cost of \$2,500 per PI is requested per annum for a total of \$12,500 to support various costs. This request is subject to on-campus indirect rate of 51.5\%.}

\item {{\bf Total Fringe Benefit}: The total cost for the fringe benefit is \$80,520 .}

\item {{\bf Total Indirect}: The total indirect cost computed using the proportion of the on-campus (51.5\%) and off-campus (26\%) described above is \$222,435 .}

\item {{\bf Grand Total for Year 1}: The grand total request for year 1 for ATLAS is \$840,348.}

\end{itemize}

% ATLAS - Year 2 justification 
\item{Year 2}
\begin{itemize}
\item{{\bf Senior Personnel}: Summer salary for PIs requested is \$100,139.   The fringe benefit rate is 30\% of the request.  The indirect rate for this item is the agreed on-campus rate of 51.5\%.}

\item {{\bf Postdoctoral Researcher}:  A request for 3 postdoctoral fellows is made using the base salary of \$55,620 per annum for a total of\$172,422 .  The fringe benefit rate is 30\% of the request.  Since it is anticipated to have 1 postdoctoral fellow on-campus and 2 off campus at CERN, the indirect rates for this cost are 26\% off-campus and 51.5\% on-campus for the relevant portion of the cost.} 

\item{{\bf Graduate Students}: A request for 4 graduate students support is made at the base rate of \$24,720 per annum for a total of \$98,880.   The fringe benefit rate is 10\% of the request.  Since it is anticipated to have 2 graduate students on-campus and 2 off-campus at CERN, indirect rate for this cost 51.5\% and 26\% respectively.}

\item {{\bf Undergraduate Students}: A request of 3 undergraduate students support is made at the base rate of \$5,000 per annum for a total of \$15,000. They will be located on-campus therefore an indirect rate of 51.5\% is applied to this rate. }

\item{{\bf Travel and Cost of Living Adjustment}:  A request of total of \$110,700 for travel and COLA support for postdoctoral fellow and graduate student is made. Of this amount, the travel support is \$49,500.  An indirect rate for this cost of 26\% off-campus is applied. }

\item {{\bf STEM Tuition}: Graduate student tuition support for one student is requested at the rate of \$9,140 per annum for a total of \$36,560.  This cost does not incur indirect cost.}

\item {{\bf M\&O}: A modest request for maintenance and operation cost of \$2,500 per PI is requested per annum for a total of \$12,500 to support various costs. This request is subject to on-campus indirect rate of 51.5\%.}

\item {{\bf Total Fringe Benefit}: The total cost for the fringe benefit is \$82,891.}

\item {{\bf Total Indirect}: The total indirect cost computed using the proportion of the on-campus (51.5\%) and off-campus (26\%) described above is \$227,849.}

\item {{\bf Grand Total for Year 2}: The grand total request for year 2 for ATLAS is \$856,134.}

\end{itemize}

% ATLAS - Year 3 justification 
\item{Year 3}
\begin{itemize}
\item{{\bf Senior Personnel}: Summer salary for PIs requested is \$103,143.   The fringe benefit rate is 30\% of the request.  The indirect rate for this item is the agreed on-campus rate of 51.5\%.}

\item {{\bf Postdoctoral Researcher}: A request for 4 postdoctoral fellows is made using the base salary of \$57,289 per annum for a total of \$206,239.  The fringe benefit rate is 30\% of the request.  Since it is anticipated to have 1 postdoctoral fellow on-campus and 3 off campus at CERN, the indirect rates for this cost are 26\% off-campus and 51.5\% on-campus for the relevant portion of the cost.} 

\item{{\bf Graduate Students}: A request for 5 graduate students support is made at the base rate of \$25,462 per annum for a total of \$114,577.  The fringe benefit rate is 10\% of the request.  Since it is anticipated to have 3 graduate students on-campus and 2 off-campus at CERN, indirect rate for this cost 51.5\% and 26\% respectively.}


\item {{\bf Undergraduate Students}: A request of 3 undergraduate students support is made at the base rate of \$5,000 per annum for a total of \$15,000. They will be located on-campus therefore an indirect rate of 51.5\% is applied to this rate. }

\item{{\bf Travel and Cost of Living Adjustment}: A request of total of \$116,700 for travel and COLA support for postdoctoral fellow and graduate student is made. Of this amount, the travel support is \$49,500.  An indirect rate for this cost of 26\% off-campus is applied. }

\item {{\bf STEM Tuition}: Graduate student tuition support for one student is requested at the rate of \$9,140 per annum for a total of \$41,130.  This cost does not incur indirect cost.}

\item {{\bf M\&O}:  A modest request for maintenance and operation cost of \$2,500 per PI is requested per annum for a total of \$12,500 to support various costs. This request is subject to on-campus indirect rate of 51.5\%.}

\item {{\bf Total Fringe Benefit}:  The total cost for the fringe benefit is \$ 97,745.}

\item {{\bf Total Indirect}: The total indirect cost computed using the proportion of the on-campus (51.5\%) and off-campus (26\%) described above is \$252,816.}

\item {{\bf Grand Total for Year 3}: The grand total request for year 3 for ATLAS is \$960,405.}

\end{itemize}
\end{enumerate}

\newpage
