\textbf{Energy Frontier - International Linear Collider}

\item{\bf Year 2}

\begin{itemize}

\item{{\bf Senior Personnel}: One month summer salary for White is requested at the current rate of \$131,208 per 9 month academic year, 
equivalent to \$14,579 per month.  The total request for this item is two summer months at \$14,579. The fringe benefit rate is 30\% of the request.  
The indirect rate for this item is the agreed on-campus rate of 51.5\%.}

\item {{\bf Undergraduate Students}: Undergraduate students Andrew Myers and Ross McCoy will continue their present work on the SiD simulation.
Support for two undergraduates is requested at the base rate \$5,000, equivalent to \$12.5 per hour, 10 hours a week for 40 weeks per year.  
The total cost for this request is \$10,000.  The fringe benefit rate for an undergraduate student is 8.5\%.}

\item{{\bf Travel}: A total of \$14,000 is requested to support White's travel as SiD Spokesperson - 1 trip to Japan at \$3,000, 1 trip to
Europe at \$3,000, both of these for regional LC meetings and SiD recruiting; 1 international conference at \$3,000, one domestic conference 
at \$2,500, and one domestic SiD Workshop at \$2,500.}

\item {{\bf M\&O}: A limited amount for maintenance and operation cost of \$2,500 per annum is requested to support various costs.   
This request is subject to on-campus indirect rate of 51.5\%.}

\item {{\bf Total Fringe Benefit}: The total cost for the fringe benefit is \$5,224.}

\item {{\bf Total Indirect}: The total indirect cost computed using the on-campus (51.5\%) and off-campus (26\%) rates is \$18,988}

\item {{\bf Total for Year 2}: The total request for Year 1 ILC for White is \$62,790.}

\end{itemize}