\bibitem{Sauli}
  R. Bouclier, {\it et al.}, "The Gas Electron Multiplier (GEM),"
  IEEE Trans. Nucl. Sci. NS-44, 646 (1997);  F. Sauli "GEM: A New Concept
  for Electron Amplification in Gas Detectors", Nucl. Inst. Meth., A
  {\bf 386}, 531 (1997).
  
\bibitem{HinvRun1} "Search for invisible decays of a Higgs boson using vector-boson fusion 
  in $pp$ collisions at $\sqrt{s}=8$ TeV with the ATLAS detector",  JHEP 01 (2016) 172.
  
\bibitem{LHCP2015} "Search for Invisible Decays of the Higgs boson at the LHC"
   Andrew P. White, on behalf of the ATLAS and CMS Collaborations", in Proceedings of the
   LHCP2015 Conference, St. Petersburg, Russia.
   
\bibitem{HAWK} "Electroweak corrections to Higgs-strahlung off W/Z bosons at the Tevatron and the LHC with HAWK",
   A. Denner, {\it et al.}, JHEP 03  (2012) 075.
   
\bibitem{Powheg} P. Nason and C. Oleari, JHEP 1002 (2010) 037, arXiv:0911.5299

\bibitem{Run2PDF} "PDF4LHC recommendations for LHC Run II", CERN-PH-TH-2015-249.

\bibitem{SiDDBD} http://www.linearcollider.org/ILC/physics-detectors/Detectors/Detailed-Baseline-Design

\bibitem{SiDDet} {SiD Detector Concept: \\
  \tt http://silicondetector.org/display/SiD/home}
  
\bibitem{P5Report} http://science.energy.gov/~/media/hep/hepap/pdf/May-2014/FINAL_P5_Report_053014.pdf

\bibitem{FacilitiesReport} http://science.energy.gov/~/media/hep/hepap/pdf/Reports/HEPAP_facilities_letter_report.pdf

\bibitem{RMPCALICE} "Experimental tests of particle flow calorimetry", F. Sefkow, A. White, Kiyotomo Kawagoe, Roman Pöschl, 
  and José Repond, Rev. Mod. Phys. 88, 015003 (2016).
  
\bibitem{GEMDHCAL} "Development of GEM-based Digital Hadron Calorimetry using the SLAC KPiX chip", A. White, 2010 JINST 5 P01005.

\bibitem{DD4HEP} "DD4hep: A Detector Description Toolkit for High Energy Physics Experiments", M. Frank, F. Gaede, C. Grefe1 and P Mato, 
  Journal of Physics: Conference Series, Volume 513, Track 2.
  

\bibitem{LAPPD} http://hep.uchicago.edu/~frisch/#Psec; arXiv:1603.01843v1
\bibtem{incom}
\bibitem {Photonis} http://www.photonis.com.
\bibitem{life} T. W. Estrera and J. P. Sinor, ``An Analysis of Electron Scattering in Thin Dielectric Films Used as Ion Barriers in Generation III Image Tubes," Proceedings of SPIE, vol. 4796, pp. 23-32, 2003. 
\bibitem{DIRC} 
I. Adam et al., Nucl. Instrumen. Meth., vol. A538, p. 281, 2005. 
\bibitem{Nagoya} 
M. Akatsu et al., Nucl. Instrumen. Meth., vol. A440, pp. 124-135, 2000. 
\bibitem{Nagdet} 
K. Inami et al., Nucl. Instrumen. Meth., vol. A560, pp. 303-308, 2006. 
\bibitem{TOF} 
[Online]. Available: http://inspirehep.net/record/642172/files/fermilab-conf-03-404.pdf.
[8] 
N. Kishimoto et al., Nucl. Instrumen. Meth., vol. A564, p. 204, 2006. 
[9] 
J. Va'vra, "Optical Components for Cherenkov Detectors," in 8th International Workshop on Ring Imaging Detectors (RICH2013), Hayama, Kanagawa, Japan, 2013. 
[10] 
A. Lehmann, "Tremendously Increased Lifetime of Microchannel-Plate PMTs," in VCI2016 - The 14th Vienna Conference on Instrumentation , Vienna, Austria.
\bibitem{FP420} 
M. G. Albrow et al., ``The FP420 R\&D Project: Higgs and New Physics with Forward Protons at the LHC," JINST, vol. 4, p. T10001, 2009. 
\bibitem{ALD}


\bibitem{Nagprod} K. Matsuoka et al.  Nucl. Instr. and Meth. A 766 (2014) 148 bibitem{Nagald} K. Matsuoka et al.  International Conference on New Photo-detectors, PhotoDet2015 6-9 July 2015 Moscow, Troitsk, Russia.
.
